The low-frequency Murchison radio environment:\\interference analysis and mitigation

### 2014-10-22 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Some more work on the article

In the ideal case, the residual visibility distributions show a smooth Rayleigh curve (see \citealt{offringa-rfi-distributions}). The tails of the residual curves of Fig.~\ref{fig:lognlogs} are however not smooth. Especially in the case of the EoR high-band and low-band observations, the residual curve shows RFI that has not been properly detected as such. In the case of EoR low-band, samples are not detected as RFI even though they are an order of magnitude brighter than where the GLEAM residual curve ends. The reason such samples leak through detection is because the detection strategy includes a bandpass correction per 1.28-MHz sub-band. When RFI persistently contaminates approximately a full subband, its effect will be absorbed in the bandpass correction and becomes invisible for the flagger. In some cases, this will cause the calibration to fail on those channels, after which it will be flagged nevertheless. In other cases, such RFI is included in the imaging step or further processing, which is obviously very undesirable.

The distribution curves do not show a very significant power-law tail. The EoR high-band observes too little RFI to generate such a power law, which is reflected by its fit of $N=\beta S^{-4.47}$, with $\beta$ being an arbitrary scaling factor. The GLEAM and EoR low-band observations do show a small power-law part, but the fitted exponent depends strongly on what part of the tail is selected. Fits over by-eye selected regions have been added, with $N=\beta S^{-1.43}$ and $N=\beta S^{-1.33}$ for the GLEAM and Eor-low curves of Fig.~\ref{fig:lognlogs}, respectively.

>>>>

In the ideal case, the residual visibility distributions show a smooth Rayleigh curve (see \citealt{offringa-rfi-distributions}). However, especially the tails of the residual curves of the EoR high-band and low-band observations are not smooth in Fig.~\ref{fig:lognlogs}, and the residual curve shows RFI that has not been properly detected as such. In the case of EoR low-band, samples are not detected as RFI even though they are an order of magnitude brighter than the brightest samples in the GLEAM observations. The reason such samples leak through detection is because the detection strategy includes a bandpass correction per 1.28-MHz sub-band. When RFI persistently contaminates approximately a full subband, its effect will be absorbed in the bandpass correction and becomes invisible for the flagger. In some cases, this will cause the calibration to fail on those channels, after which it will be flagged nevertheless. In other cases, such RFI is included in the imaging step or further processing, which is obviously very undesirable.

The distribution curves do not show a very significant power-law tail. Fits over regions selected by eye have been added to Fig.~\ref{fig:lognlogs}. The EoR high-band observes too little RFI to generate such a power law, which is reflected by its fit of $N=\beta S^{-4.47}$, with $\beta$ being an arbitrary scaling factor. The GLEAM and EoR low-band observations do show a small power-law part, but the fitted exponent depends strongly on what part of the tail is selected. The selected regions result in $N=\beta S^{-1.43}$ and $N=\beta S^{-1.33}$ for the GLEAM and Eor-low curves, respectively.
